In-Band Synchronization for\\Distributed SDN Control Planes\thanks{Supported by the European Institute of Innovation \& Technology (EIT) project 13153 (Software Defined Networking) and the FP7 EU project UNIFY.}

### 2015-11-16 ccr-camera/inband-sync.tex
typos

A less trivial Algorithm~\ref{alg:update} adresses the problem of
policy identifiers growing without bound in  
Algorithm~\ref{alg:simple-update} by, additionally, using our id-claimer abstraction.
%to bound the number of used policy identifiers.
Here, the controller first reads the current policy id and 
claims it, which prevents another controller from using the id 
for a different policy (Lines~\ref{update:read-state1}-\ref{update:read-state2}).Then the controller claims the first \emph{unused} id and computes the update commands to be executed (Line~\ref{update:compute}).
Finally, within an atomic transaction (\textbf{\execatomic}), it verifies whether the chosen policy id has not
been claimed and that
the policy has not been concurrently modified, and then updates the
policy.
Unlike Algorithm~\ref{alg:simple-update}, this algorithm is only
\emph{lock-free}, as it allows scenarios in which only one live controller
succeeds in installing its updates. We can easily make it
wait-free by

@@

For instance, we experimented with a setting where three processes
(controllers) issue thousands of concurrent policy updates
to the switch, 
each update consisting in replacing a single rule with another one.
%[[PK unclear
%When verifying the transactions, 
%]]
We could confirm that 
despite the concurrency, 100 \% of the updates have been
eventually completed.
Of course, due to the concurrency, some transactions also needed to abort
because of conflicts.

>>>>

A less trivial Algorithm~\ref{alg:update} adresses the problem of
policy identifiers growing without bound in  
Algorithm~\ref{alg:simple-update} by, additionally, using our id-claimer abstraction.
%to bound the number of used policy identifiers.
Here, the controller first reads the current policy id and 
claims it, which prevents another controller from using the id 
for a different policy (Lines~\ref{update:read-state1}-\ref{update:read-state2}).Then the controller claims the first \emph{unused} id and computes the update commands to be executed (Line~\ref{update:compute}).
Finally, within an atomic transaction (\textbf{\execatomic}), it verifies whether the chosen policy id has not
been claimed and that
the policy has not been concurrently modified, and then updates the
policy.
%[[PK 
%We observe that our  algorithm is only
%\emph{lock-free}, as it allows scenarios in which only one live controller
%succeeds in installing its updates. We can easily make it
%wait-free by reading the state of the switch and claiming the current
%policy id within the same {\execatomic} construct.
%]]

@@

For instance, we experimented with a setting where three processes
(controllers) issue thousands of concurrent policy updates
to the switch, 
each update consisting in replacing a single rule with another one.
%[[PK unclear
%When verifying the transactions, 
%]]
We could confirm that 
despite the concurrency, 100 \% of the transactions have been
eventually completed.
Of course, due to the concurrency, some transactions also needed to abort
because of conflicts. 
\petr{Reads strange: 100\% successfullt complete and some transactions
  abort...}
